Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2017-03-09 paper/propane/SOSR/propane.tex
add sosr extended abstract

%\documentclass{sig-alternate-10pt}
\documentclass[10pt]{sigalternate052015}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
%\usepackage{geometry}

\usepackage{balance}

@@

\CopyrightYear{2016} 
\setcopyright{acmcopyright}
\conferenceinfo{SIGCOMM '16,}{August 22-26, 2016, Florianopolis , Brazil}
\isbn{978-1-4503-4193-6/16/08}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2934872.2934909}

@@

\author{%
Ryan Beckett\\
  \affaddr{Princeton}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{UCLA}
  %\affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitendra Padhye\\
  \affaddr{Microsoft}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton}
  %\\
  %\email{dpw@princeton.edu}
}

\maketitle

@@

%=====================================================
%
%
%  **Keywords**
%
%
%=====================================================

%\category{CR-number}{subcategory}{third-level}

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10003033.10003068.10003073.10003075</concept_id>
%<concept_desc>Networks~Network control algorithms</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10003033.10003083.10003095</concept_id>
%<concept_desc>Networks~Network reliability</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10003033.10003099.10003104</concept_id>
%<concept_desc>Networks~Network management</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
%<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10011006.10011050.10011017</concept_id>
%<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[300]{Networks~Network control algorithms}
%\ccsdesc[300]{Networks~Network reliability}
%\ccsdesc[300]{Networks~Network management}
%\ccsdesc[300]{Software and its engineering~Automated static analysis}
%\ccsdesc[300]{Software and its engineering~Domain specific languages}
%
%\printccsdesc
%
%\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}

\vspace{0.1in}
\noindent
\textbf{CCS Concepts}\\
$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;} 
$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}

\vspace{0.1in}
\noindent
\textbf{Keywords}\\
Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems

%% general terms are not compulsory anymore,
%% you may leave them out
%\terms Network Programming Language, Distributed Program Synthesis
%\keywords Propane Language, BGP, Synthesis, Compilation

@@

%=====================================================
%
%
%  **Background**
%
%
%=====================================================

\section{Background on BGP}
\label{sec:background}

%Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.

BGP is a path-vector routing protocol that connects autonomous systems (ASes). An AS has one or more routers managed by the same administrative entity. ASes exchange routing announcements with their neighbors. Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic destined to that prefix from the receiving AS. Traffic flows in the opposite direction, from announcement receivers to senders.

When a route announcement is received by an AS, it is processed by custom import filters that may drop the announcement or modify some attributes. If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy (see below). This route is then used to send traffic to the destination. It is also advertised to the neighbors, after processing through neighbor-specific export filters that may stop the announcement or modify some attributes.

All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far. While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.  One such attribute is a list of community strings. ASes use such strings to associate network-specific information with particular routes (\EG, ``entered on West Coast'') and then use the information later in the routing process.  Communities are also used to signal to neighbors how they should handle an announcement (\EG, do not export it further). Another non-global attribute is the multi-exit discriminator (MED). It is used when an AS has multiple links to a neighboring AS.  Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.

The route selection process assigns a {\em local preference} to each
route that survives the import filters. Routes with higher local
preference are preferred. Among routes with the same local preference,
other factors such as AS path length, MEDs, and internal routing cost, are considered in order. Because it is considered first during route selection, local preference is highly influential, and ASes may assign this preference based on any aspect of the route. A common practice is to assign it based on the commercial relationship with the neighbor. For instance, an AS may prefer in order customer ASes (which pay money), peer ASes (with free exchange of traffic), and provider ASes (which charge money for traffic).

The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol. That flexibility, however, comes at the cost of it being difficult to configure correctly.
When configuring BGP, network operators assume that
neighboring ASes correctly implement BGP and honor contracts for MEDs and communities. \sysname makes the same assumption when
deriving BGP configurations for a network.

%=====================================================
%
%
%  **Motivation**
%
%
%=====================================================

\section{Motivation}
\label{sec:motivation}

%We motivate our work by describing the current practice in network
%configuration. In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy. This configuration dictates the behavior of a device, how it exchanges routing information with neighbors and how it filters and ranks that information. The collective behavior of the devices should implement the desired policy.
%
%Device configuration languages are low-level and indirect. For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify metrics that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., BGP import or export filters, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
%
%In many networks today, device configurations are generated manually by operators, without the support of many automated tools. It is easy to see the problems with this approach, such as typos, inconsistency across devices, and no guarantees of policy compliance.
%
%To reduce such problems, some networks use a template-based approach. Configuration templates abstract certain constants into variables (e.g., instead of concrete community value, they may contain a variable {\small \sf{\$$BadNeighbor$)}} and may use a device vendor-neutral syntax. Operators manually generate the templates and use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
%
% %and replacing vendor-neutral constructs with their vendor-specific counterparts.
%
%%In practice, most networks use a hybrid of templates and manual generation of device configuration. Templates are used for standardized and common configuration elements across devices and the result is manually tweaked to obtain the exact desired network behavior.
%
%While templates avoids some pitfalls of the fully manual approach, they too are far from ideal. The fundamental issue is the semantic mismatch between desired policies and the level of abstraction of templates. While many policies are network-wide (e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors), templates are device-level. Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
%This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures. We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
%examples are described using our new language \sysname.

%Operators today generate the BGP configuration of individual devices based on intended policy.
When generating BGP configurations, whether manually or aided by templates, the operators face the challenge of decomposing network-wide policies
into correct device-level policies.
This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures. In this section, we illustrate this difficulty using two examples based on policies that we have seen in practice. The next section shows how \sysname allows operators to express these policies naturally.
%the ease with which the
%policies can be specified using our new language \sysname.
%The next section describes how to automatically compile this specification to device-level policies.

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example1}
  \caption{Creating router-level policies is difficult.}
  \label{fig:example1}
  \vspace{-1em}
\end{figure}

\subsection{Example 1:  The backbone}

Consider the backbone network in Figure~\ref{fig:example1}. It has
three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}. The policy of this network is shown on the right. It prefers that traffic leave the network through neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2). It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3). To guard against another AS "hijacking" prefixes owned by \CD{Cust}, the network only sends traffic to a neighbor if \CD{Cust} is on the AS path (P4). Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).

To implement policy P1, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3, the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 will also require MEDs to be appropriately configured on \CD{R1} and \CD{R2}.
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. A similar type of policy must be configured for \CD{R2} as well. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.

Clearly, it is difficult to correctly configure even this
small example network manually; correctly configuring real, larger networks can quickly become a nightmare. Such networks have hundreds of neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example2}
  \caption{Policy-compliance under failures is difficult.}
  \label{fig:example2}
  \vspace{-1em}
\end{figure}

\subsection{Example 2:  The datacenter}

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the datacenter network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, datacenter networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

The operator may implement the policy by having X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ export externally what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}. This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can occur independently, \EG, local services can be assigned new prefixes without updating those routers' configurations.

However, this implementation has incorrect behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per its policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (\EG, if the services are sensitive) or availability (\EG, if the \CD{PL*} prefixes are reused for other services outside of the datacenter). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will occur if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in datacenters are frequent and it is not uncommon to have many failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may disallow "valley" paths, \IE, those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced black hole~\cite{route-aggregation}. If links D--A and X--C fail, X will hear an announcement for \CD{PG2} from D and will thus announce \CD{PG} externally. This announcement will bring traffic for \CD{PG1} to X as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic for it despite the fact that a valid path exists through $Y$.

Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone. \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures if possible---otherwise, it generates a compile-time error. For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in black holes.

%\subsection{OLD -- Overview}
%\todo{this subsection can be deleted once we have captured everything in it}
%
%Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
%Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
%
%\begin{itemize}
% \item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
% \item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
% \item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
% \item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
% \item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
%\end{itemize}
%
%
%Possible Examples:
%\begin{itemize}
% \item Basic datacenter with spine preference
% \item Simple AS that prefers customers over peers over providers
% \item Combined internal backup routing with preference based entrance into the network using aggregation.
% \item Something like cold potato routing
%\end{itemize}

%=====================================================
%
%
%  **Propane Language**
%
%
%=====================================================

\section{Propane overview}
\label{sec:propane}

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, they must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (\EG,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on the topology.
%

This section introduces the \sysname language using the
examples from the previous section.
%, introducing key aspects of
%the \sysname language along the way.
The next section describes the complete syntax of the
language as well as our strategy for compiling it to
BGP.

\subsection{Example 1: The backbone}

%\sysname simplifies network configuration by allowing users to
%specify end-to-end forwarding paths and associating them with
%appropriate prefixes.  The \sysname compiler handles the task of
%generating low-level BGP configurations consistent with the user's
%specifications.  It automatically synthesizes
%import-export filters, local preferences, MED attributes, and community tags
%to ensure policy compliance under all possible failure scenarios.

\sysname lets operators configure the network with the
abstraction that they have centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the
paths traffic should---or should not---take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that
we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P1 and P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
leave through \CD{Peer} and then \CD{Prov}.  As we
describe in the next section, the \Exit\ expression, as well as other
path expressions used later in this section, is simply a shorthand for
a particular regular expression over paths that is expressible in our policy
language. The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers. For example, the above constraint could have been written equivalently as
\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})

To associate ranked paths with
one or more prefixes, we define a \sysname \emph{policy}.
Within a policy, statements with the form $t\;$\Path$\;p$
associate the prefixes defined by the predicate $t$ with the set of
ranked paths defined by the path expression $p$.  In general,
prefix predicates can be defined by arbitrary boolean combinations
(and, or, not) of concrete prefixes and community tags.  Here,
we assume we have already defined the predicate \CD{PCust} for the
customer prefixes.
%and \CD{PInt} for our internal prefixes.
In the following code, ranked paths are associated with
customer prefixes,
and all other prefixes (\CD{true}). Policy statements are processed in
order with earlier policy statements taking precedence over later
policy statements. Hence, when the predicate \True{} follows
the statement involving \CD{PCust}, it is interpreted as
\CD{\True{} \AND{} \NOT{}PCust}.

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
%%     $\path{I_{pfx}}{end(in)}$
%%     $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
%% }
%% \end{lstlisting}

\begin{code}
\Define Routing =
    \{PCust \Path Prefs \AND \End(Cust)
     \True  \Path Prefs \}
\end{code}
\noindent

Line 2 of this policy
restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer. In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
%defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
%that connections to the customer through both routers fail,
%a backup route (\CD{\End(Cust)}) is defined that admits traffic along
%any path (including those through other networks) that ends at the customer.
%Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preference of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

Since, routing allows transit traffic by default (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints.
First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
\begin{code}
\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
\end{code}
\noindent
Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.

\begin{code}
\Define NoTrans =
  \{\True \Path \NOT{}transit(Peer,Prov) \AND
           \NOT{}cust-transit(Cust,Prov)\}
\end{code}
\noindent
The \CD{NoTrans} constraint requires that all traffic not follow a path that transits our network between \CD{Peer} and \CD{Prov}.
Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%

Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failures.

\subsection{Example 2: The datacenter}

Our datacenter example network has three main concerns:
(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the datacenter, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

\sysname allows modular specification of each of these constraints. The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location. The following definition captures this intent.

%% \begin{lstlisting}[mathescape=true]
%% define Ownership = {
%%     $\path{p_{g1}}{end(A)}$
%%     $\path{p_{g2}}{end(B)}$
%%     $\path{p_{l1}}{end(E)}$
%%     $\path{p_{l2}}{end(F)}$
%% }
%% \end{lstlisting}

\begin{code}
\Define Ownership =
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
end at router \CD{A}; traffic for \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.

For the second constraint, we define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality =
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself.
%This means traffic for
%\CD{PG*} may be sent either from other datacenter routers or
%from external ASes.
This definition says that traffic for local
prefixes only follows paths that are internal to the network at each hop.
This constraint guarantees that the services remain accessible only to locations
inside the datacenter.

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
However, in addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane itself.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out).
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
(which we assume is defined earlier)
when advertised outside the datacenter.

\begin{code}
Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
\end{code}

Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes. In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.

%%%%OLD TEXT BELOW
%\section{Propane}
%\label{sec:propane}
%\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy.
%The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
%The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
%We now demonstrate \sysname by showing how to configure the networks from the previous examples.
%\para{Example 1}
%We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}. \sysname allows to address each of the requirements in turn. First we address requirements (P1), (P3), and (P4) that customers are preferred over peers over providers, and that a customer appear on the path for its prefix. The following \sysname code accomplishes these two objectives:
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%define Routing = {
%    $\path{C_{pfx}}{ExitCust \gg end(Cust) }$
%    $\path{I_{pfx}}{end(in)}$
%    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
%}
%\end{lstlisting}
%The first definition defines paths that exit our network to the customer. The statement $exit(R_1 \gg R_2)$ restricts us to paths that leave our network through either router $R_1$ or $R_2$, with a preference for $R_1$.
%The first line of the \textsf{Routing} policy ensures that traffic destined for customer prefixes ($C_{pfx}$) either leaves the network directly to the customer (with a preference for leaving through $R_1$), or simply ends at the customer. Not leaving directly to the customer by going through \textit{Peer} or \textit{Prov} is less preferred than leaving directly, and thus serves as a backup route in a direct route is not available.
%The second line state that traffic for internal prefixes $I_{pfx}$ must end in our network, and is otherwise unconstrained. The last line applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers. While this still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can restrict this behavior separately as follows:
%\begin{lstlisting}[mathescape=true]
%define PP = Peer or Prov
%define PPTransit = $enter(PP) \wedge exit(PP)$
%define CustTransit = $later(Cust) \wedge later(Prov)$
%define NoTransit = {
%    $\path{true}{\neg PPTransit \wedge \neg CustTransit}$
%}
%\end{lstlisting}
%The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied. In particular, it says that, for any prefix, traffice should never both enter and exit the network from \textit{Peer} or \textit{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later go through both \textit{Prov} and \textit{Cust}.
%\begin{lstlisting}[mathescape=true]
%Routing $\wedge$  NoTransit
%\end{lstlisting}
%The final policy is simply the conjunction of the routing and no transit constraints. \sysname will generate per-device import and export filters, local preferences and MED attributes, and community tags to ensure that the policy is met under all failure scenarios.
%\para{Example 2}
%Consider again the datacenter from Section~\ref{sec:motivation}. In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
%\sysname allows us to decompose and specify each of these constraints in a modular fashion. The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations. The following definition in propane captures this intent:
%\begin{lstlisting}[mathescape=true]
%define Ownership = {
%    $\path{p_{g1}}{end(A)}$
%    $\path{p_{g2}}{end(B)}$
%    $\path{p_{l1}}{end(E)}$
%    $\path{p_{l2}}{end(F)}$
%}
%\end{lstlisting}
%The constraints in the ownership task are read in a top-down fashion. Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A. Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
%To capture the second constraint, we can define another task for the core routing policy:
%\begin{lstlisting}[mathescape=true]
%define Routing = {
%    $\path{p_{g*}}{any}$
%    $\path{p_{l*}}{\neg enter(out)}$
%    $\path{true}{exit(out)}$
%}
%\end{lstlisting}
%The first line states that there is no restriction on how traffic must traverse the network for global prefixes. This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes. The second line ensures that traffic for local prefixes never enters the network from an outside location. This  guarantees that the services remain reachable only to locations internal to the datacenter.
%Finally, we can combine these constraints logically to specify the network-wide policy:
%\begin{lstlisting}[mathescape=true]
%Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
%\end{lstlisting}
%In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane. Above, a constraint on aggregation is included to ensure that an aggregation for $p_{agg}$ is performed from locations inside the network to locations outside the network.
%Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.

%=====================================================
%
%
%  **Compilation**
%
%
%=====================================================

\section{Compilation}
\label{sec:compilation}

The examples above use what we call the front end (FE) of \sysname.
It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity. The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.

\begin{figure}[t!]
  \centering
  \includegraphics[width=.75\columnwidth]{figures/pipeline}
  \caption{Compilation pipeline stages for Propane.}
  \label{fig:pipeline}
  \vspace{-1em}
\end{figure}

% grammar
\newcommand{\BNFALT}{\;\;|\;\;}
\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}

\begin{figure*}[t]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline

     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     x       &::=& d.d.d.d/d & \textit{prefix} \\
     t       &::=& \True & \textit{true} \\
         &\BNFALT& \NOT t & \textit{negation} \\
         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
         &\BNFALT& \textit{comm} = d & \textit{community test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     ln       &::=& r_1 \rightarrow r_2 & \textit{links} \\
     cc     &::=& agg(x, ln) \BNFALT tag(d, t, ln) & \textit{control constraints} \\
  \end{array} \]

>>>>

%\documentclass{sig-alternate-10pt}
\documentclass[10pt]{acmart}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{xspace}
\usepackage{code}
%\usepackage{geometry}
%\usepackage{balance}

@@

@@

%\author{%
%Ryan Beckett\\
%  \affaddr{Princeton}
%  %\\
%  %\email{rbeckett@princeton.edu}
%\and
%Ratul Mahajan\\
%  \affaddr{Microsoft}
%  %\\
%  %\email{ratul@microsoft.com}
%\and
%Todd Millstein\\
%  \affaddr{UCLA}
%  %\affaddr{University of California, Los Angeles}
%  %\\
%  %\email{todd@cs.ucla.edu}
%\and
%Jitendra Padhye\\
%  \affaddr{Microsoft}
%  %\\
%  %\email{padhye@microsoft.com}
%\and
%David Walker\\
%  \affaddr{Princeton}
%  %\\
%  %\email{dpw@princeton.edu}
%}

%\maketitle

@@

@@
